A longitudinal dataset of childhood gut microbiome linked with cognitive evaluation

### 2021-05-07 manuscript/main.tex
more types, links to repos

\author[1]{Kevin S Bonham}
\author[1]{Shelley Hoeft McCann}
\author[1]{Sophie Rowland}
\author[2]{Alexandra R. Volpe}
\author[2]{Kellyn Dyer}
\author{RESONANCE Consortium}
\author[2,3]{Viren D’Sa}
\author[2,3,5,6]{Sean C. L. Deoni}
\author[1,*]{Vanja Klepac-Ceraj}

@@

The gut, the gut microbiome, and the central nervous system are intricately linked
through a system known as the gut-microbiome-brain axis \cite{Clarke2013-yu},
and differences in microbial communities are associated with, and in some cases cause,
changes in neurocognitive development \cite{Flannery2020-de, Gao2019-je}.
and the outcome of neurological disorders such as autism \cite{Sharon2019-ak}.
However, the study of the relationships between environmental exposures, neurocognitive development,
and the gut microbiome during neurotypical development remains in its infancy \cite{Carlson2018-iw,Sordillo2019-wi}.

>>>>

\author[1]{Kevin S. Bonham}
\author[1]{Shelley Hoeft McCann}
\author[1]{Sophie Rowland}
\author[2]{Alexandra R. Volpe}
\author[2]{Kellyn Dyer}
\author{RESONANCE Consortium}
\author[2,3]{Viren D’Sa}
\author[2,3,5,6]{Sean C. L. Deoni}
\author[1,*]{Vanja Klepac-Ceraj}

@@

The gut, the gut microbiome, and the central nervous system are intricately linked
through a system known as the gut-microbiome-brain axis \cite{Clarke2013-yu},
and differences in microbial communities are associated with, and in some cases cause,
changes in neurocognitive development \cite{Flannery2020-de, Gao2019-je},
and the outcome of neurological disorders such as autism \cite{Sharon2019-ak}.
However, the study of the relationships between environmental exposures, neurocognitive development,
and the gut microbiome during neurotypical development remains in its infancy \cite{Carlson2018-iw,Sordillo2019-wi}.
